Finding points on varieties with \emph{Macaulay2}

### 2021-08-19 FastLinAlg/Paper/RandomRationalPoints.tex
clarifications, almost done with the package documentation changes

    There is an existing package called {\tt RationalPoints} \cite{RationalPointsSource}, which we took inspiration from, which aims to find \emph{all} the rational points of a variety; our aim here is to find one or more points quickly, even if it is not rational.  We also note that the package {\tt Cremona} \cite{CremonaSource} can find rational points on projective varieties, as can the core function {\tt randomKRationalPoint} \cite{M2} -- our methods frequently appear to be faster and apply in the affine setting as well.

>>>>

    There is an existing package called {\tt RationalPoints} \cite{RationalPointsSource}, which we took inspiration from, which aims to find \emph{all} the rational points of a variety; our aim here is to find one or more random rational or geometric points on a variety quickly.  We also note that the package {\tt Cremona} \cite{CremonaSource} can find rational points on projective varieties, as can the core function {\tt randomKRationalPoint} \cite{M2} -- our methods frequently appear to be faster and apply in the affine setting as well.
